\documentclass{letter}
\signature{UMass CS Women Co-Chairs Cassian Corey, Myung-ha Jang, Emma Tosch, Niharika Venkatathri}

\address{21 Bridge Street \\ Smallville \\ Dunwich DU3 4WE}

\begin{document}

\opening{To Whome It May Concern:}{Director \\ Doe \& Co \\ 35 Anthony Road
\\ Newport \\ Ipswich IP3 5RT}

UMass CS Women is a student-run organization of over 50 members, housed in the University of Massachusetts School of Computer Science. We provide event programming for our members that ranges from professional development seminars, to technical talks, to social events. The goal of these activities is to encourage women students to participate in the computer science community by providing a fun and nurturing atmosphere. 

We are currently planning an egg drop competition as a team-building exercise, designed to foster connections between the women students and the greater computer science community. The event will be open to graduate and undergraduate computer science students. We are seeking support from our industrial affiliates in the form of prizes for this competition. 

Event details: In an egg drop competition, competitors use limited materials, such as paper, cups, bubble wrap, cotton, glue, straws, etc., to build an apparatus to protect an egg when it is dropped from a non-trivial height. Students will be asked to form and register teams before the event. We have tentatively scheduled the event for April 1st, at 4PM. The teams will have 40 minutes to brainstorm and build the device before dropping from the banister of the second floor. Attendees who are not competitors may watch from the stairwell. The goal of this event is to encourage a sense of collaboration between the members and to engage in a fun engineering challenge.
	
	\closing{Thank You,}
	
\end{document}
